DAOS and Friends: A Proposal for\\an Exascale Storage System

### 2016-07-18 paper.tex

%\title{Fast Forwarding Storage for Extreme Scale Platforms and Big Data Applications}
\title{Lessons Learned from the Fast Forward Storage and I/O Project}

\author{
%\IEEEauthorblockN{Blinded for review},\IEEEauthorblockA{}
\IEEEauthorblockN{Jay Lofstead\IEEEauthorrefmark{1}, Ivo Jimenez\IEEEauthorrefmark{2}, Carlos Maltzahn\IEEEauthorrefmark{2}, Quincey Koziol\IEEEauthorrefmark{3}, John Bent\IEEEauthorrefmark{4}, Eric Barton\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Sandia National Laboratories gflofst@sandia.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{2}University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Lawrence Berkeley National Laboratory koziol@lbl.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Segate Government Solutions John.Bent@seagategov.com}
\IEEEauthorblockA{\IEEEauthorrefmark{5}Intel eric.barton@intel.com}
}
\maketitle

@@

To address these challenges, a joint effort between the US Department of
Energy's Office of Advanced Simulation and Computing and Advanced Scientific
Computing Research commissioned a project to develop a design and prototype for
an IO stack suitable for the extreme scale environment. It will be referred to
as the Fast Forward Storage and IO (FFSIO) project. This is a joint effort led
by Lawrence Livermore National Laboratory, with the DOE Data Management Nexus
leads Rob Ross and Gary Grider as coordinators and contract lead Mark Gary. The
participating labs are LLNL, SNL, LANL, ORNL, PNL, LBNL, and ANL.  Additional
industrial partners contracted include the Intel Lustre team, EMC, DDN, and the
HDF Group. This team has developed a specification
set~\cite{fastforward:2014:docs} for a future IO stack to address the
identified challenges. The first phase completed in 2014 with a second phase
currently getting underway. The core focus of the first phase was basic
functionality and design. While an idealized potential system would be the
perfect target architecture, the reality of budgets has tempered many of the
decisions. For example, extensive availability of NVRAM or SSDs on all of the
compute nodes is currently not economically feasible limiting some of the
potential design choices.  With this in mind, the second phase will refine this
design incorporating fault recovery and other features missing from the first
phase.

@@

Overall, the architecture shifts from the idea of files and directories to
containers of objects. This shift avoids the bottlenecks related to the POSIX
files and directories structure such as the serialization of file creation, the
limitation and impact of the number of files in a directory, and the limited
semantics of a byte stream. Instead, the new interface focuses on high-level
data models and their properties and relationships. This concept permeates the
entire IO stack.

In addition to addressing the traditional scientific workload, this project
seeks to expand functionality to better support Big Data type applications. The
key idea is to support Arbitrary Connected Graphs (ACGs) such as those used in
Map-Reduce systems. Key system features are introduced to efficiently support
these computing models in addition to the typically bursty IO loads of more
traditional HPC applications.

@@

The rest of the paper is organized as follows. An overview of related work is
presented first in Section~\ref{sec:related}. Section~\ref{sec:end-user}
discusses the programmatic interface end users will see when interacting with
the storage array. This will be discussed in the context of the HDF5 based
example library used for the functionality demonstration. Section~\ref{sec:iof}
briefly discusses the motivation and proposal for the IO forwarding layer.
Section~\ref{sec:iod} describes the IO Dispatcher layer and the broad
functionality it offers. This will detail the pieces of the layer that are
potentially optional and mention the cross-cutting features discussed in a
later, cross-cutting section. Section~\ref{sec:daos} discusses how the DAOS
layer functions. As with the IOD layer, the cross-cutting features will be
mentioned, but discussed more fully in the cross-cutting section. The VOSD
layer is discussed in Section~\ref{sec:vosd}. In particular, the mapping
between the DAOS and VOSD layers are explored as it pertains to the physical
storage. Next is an exploration of cross-cutting features like transactions and
metadata management in Section~\ref{sec:broader}. Since these and other
features are spread across multiple layers, it makes more sense to discuss them
independently once an understanding of the overall structure has been
presented.  A demonstration of the functionality is presented in
Section~\ref{sec:evaluation}. This shows that the prototype system based on the
proposed design can function. The paper is concluded in
Section~\ref{sec:conclusion} with a summary of the broad issues covered in the
paper.

@@

\item
  API extensions to support new functionality provided by the FFSIO project.
  This includes calls for managing asynchronous request lists, performing
  asynchronous operations, creating and managing transactions, end-to-end data
  integrity, and data type and functions to support the ACG functionality more
  efficiently than the current API.

@@

Since HDF5 has traditionally offered an interface focused on files and the
internal data types, such as datasets, these concepts must be mapped onto the
proposed FFSIO data storage concepts.  This mapping is shown in
Table~\ref{tab:mapping}

\begin{table}[ht]
%    \vspace{-0.10in}
    \centering
    \caption[HDF5 to FFSIO Mapping]{HDF5 Data Model to FFSIO Data Model Mapping}
    \bigskip
%    \vspace{-0.15in}

    \begin{tabular}{|r|r|}
\hline
HDF5 & FFSIO\\
\hline
file & container \\
dataset & array \\
group & key-value store \\
attribute(s) & key-value store \\
\hline
    \end{tabular}
    \label{tab:mapping}
\end{table}

@@

The core idea for IOD is to provide a way to manage IO load that is
separate from the compute nodes and the storage array. Communication intensive
activities, such as data rearrangement, can be moved to the IOD layer
reducing the number of participants and message count. IOD has three main
purposes. First, the burst buffers work as a fast cache absorbing write
operations that then trickles out to the central storage array. It can also
be used to retrieve objects from the central storage array for more efficient
read operations and offers data filtering to make client reads more efficient.
Second, it offers the transaction mechanism for controlling data set visibility
and to manage faults that could expose an incomplete or corrupt data set to
users. These transactions are local to the IOD layer until persisted to the
DAOS layer eliminating the need for burdening the persistent storage with
transient data.  Third, data processing operations can be placed in the IOD.
These operations are intended to offer functionality like data rearrangement
and filtering prior to data reaching the central storage array.

While these ideas are not necessarily new, they are new twists on best of class
efforts for these technologies. For example, offloading the collective
two-phase data sieving from the compute nodes to reorganize data has proven
effective at reducing the total time for writing data due to fewer participants
involved in the communication patterns~\cite{lofstead:2011:nessie-staging}.
Beyond these broad items, there are many important details some of which are
examined in more detail below.

@@

\subsubsection{Container}
As mentioned above, the concept of a container is similar to that of a file in
a traditional file system. However, rather than being in a directory structure,
each container essentially is stored in a hash-space allowing direct access to
any container without regard to the current organizational context of the
file system. For example, there is no need to navigate a directory hierarchy
to name a particular container.

Functionally, a container plays the same role as a file in that it holds a
collection of presumably related data intended to be accessed and manipulated
as a unit. Since this is extended from HDF5 files, the container could also be
viewed as a directory tree of objects where each directory entry specifies
either a sub-directory (group) or some data or attribute. For the IOD layer, it
is a collection of objects. For HDF5, interpreting the objects builds the
structure.

\subsubsection{Key-Value Store}
This is the base type for the container. Since the container represents
something akin to HDF5 files, everything is stored within a hierarchical
namespace. The root namespace is represented by the base key-value store and
contains a list of all of the objects for this portion of the namespace as well
as additional key-value objects representing sub-groups for the hierarchy. Each
of those key-value store objects works identically.  Attributes are stored in a
key-value store object, but use the
multi-dimensional array and blob objects to store the values for the
attributes.

\subsubsection{Multi-Dimensional Array}
By treating arrays as a special case separate from blobs, additional
opportunities are enabled. For example, by knowing that an object is an array,
proper slicing of that array onto IO nodes can be done without involving higher
levels of the IO stack.

\subsubsection{Blob}
All other data is stored as a stream-of-bytes without regard to the actual
data type.

\subsection{Multi-Dimensional Array Data Distribution}

@@

\begin{itemize}
\item
  \textbf{contiguous}. fixed chunking, distributed in a round-robin
  fashion across the IO nodes.
\item
  \textbf{chunked}. same as above but with irregular (sparse) chunking.
\item
  \textbf{user-defined}. either contiguous or chunked, but user specifies
  where to place each individual shard.
\end{itemize}

@@

In the case of the written IOD design, it describes a fixed-sized staging area
that is partitioned on a per-application basis. As part of an application
being deployed into the platform, each application will be allocated a fixed
number of IO nodes for exclusive use during the application run. This provides
guarantees about how much burst buffer space and processing capability will be
available for the applications.

Future work will generalize this model to potentially support dynamic IO node
allocation and examine the possibility of oversubscription. It will be strictly
necessary to consider shared IO nodes for cases where the number of deployed
applications exceeds the number of IO nodes.  This first phase focuses on
extreme scale application runs that use the vast majority of a platform rather
than a capacity cluster where end-to-end performance is a lesser concern.

@@

The Distributed Asynchronous Object Storage layer serves as the traditional
parallel file system interface layer for the storage devices. This is the
consistent, global view of the underlying devices represented in this stack
by the VOSD layer.

This is the layer where the container/object model is translated into the
physical storage requirements dictated by the physical storage underneath (the
VOSD layer). The two key design elements of this layer are the handling of
epochs and the mapping of containers and objects to the underlying storage.

@@

At a more detailed level, the design for VOSD is an increment beyond the
current Lustre Object Storage Device design to incorporate the idea of shards
and the versioning aspects of transactions/epochs. For every DAOS shard, the
VOSD has information for storing and accessing the currently committed version,
the Highest Committed Epoch, as well as a staging dataset representing the
next version of the object being stored. Both of these are combined in a shard
root.

For data integrity, an intent log is maintained as part of the underlying file
system enabling fault recovery.

Beyond the functionality to incorporate and expose the copy-on-write nature
of the underlying file system and the semantics for storing and processing
shards and their associated epochs, this is largely an evolution of the
existing Lustre OSD layer.

@@

In the subsections that follow, we examine transactions and epochs, metadata
management, function and analysis shipping, and the arbitrary connected graphs
support.

@@

The second form is called multi-leader and has the IOD layer manage the
transactions. In this case, when the transaction is created, a count of clients
is provided to the IOD layer. As clients commit their changes to the container,
the reference count is reduced. Once the count reaches 0, the transaction is
automatically committed.

@@

\subsection{Metadata Management}
Metadata management has been a perennial challenge for parallel storage
systems.  Eliminating metadata management as a special case and instead
treating it just as data is a central design goal of the Fast Forward project.
This is a hybrid approach to metadata management that is halfway between
providing no inherent metadata support and having a fully integrated, but
separate metadata management system.

Eliminating metadata as a core component of a file system is not new. It has
been explored as part of the Light Weight File Systems
project~\cite{oldfield:lwfs}. In LWFS, the metadata service is explicitly
limited to a user task with the storage layer limited to data
storage/retrieval, authorization, and authentication. This approach proved
workable. Using this hybrid approach is less common~\cite{weil:2006:ceph} and
introduces other issues.

@@

While the metadata design is not fully defined, there are a few things that
are intended. For example, there will be a standard, well-known container that
is the system metadata. This includes the list of all other containers. This
container is treated like any other data in the system and striped as
appropriate. Unfortunately, this still couples the metadata to a single object
that must serialize access. If the metadata, including information about
striping and other data layout operations were separated completely from the
data path, more scalable throughput could be achieved. The real challenge of
this is introduced by the IOD, DAOS, and VOSD layers collectively. Each of
these requires some different metadata storage and the migration is invisible
to the user.  Supporting fully independent metadata with this model is
difficult. Serious thought on how to do this effectively outside the data path
will be considered for phase two.

@@

\section{Acknowledgements}

%\includegraphics[scale=0.07]{logos/doe_logo}
%\includegraphics[scale=0.30]{logos/snl_logo}
%\includegraphics[scale=0.35]{logos/nnsa_logo}
Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.

>>>>

\title{DAOS and Friends: A Proposal for\\an Exascale Storage System}

\author{
\IEEEauthorblockN{Jay Lofstead\IEEEauthorrefmark{1}, Ivo Jimenez\IEEEauthorrefmark{2}, Carlos Maltzahn\IEEEauthorrefmark{2}, Quincey Koziol\IEEEauthorrefmark{3}, John Bent\IEEEauthorrefmark{4}, Eric Barton\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Sandia National Laboratories gflofst@sandia.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{2}University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Lawrence Berkeley National Laboratory koziol@lbl.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Segate Government Solutions John.Bent@seagategov.com}
\IEEEauthorblockA{\IEEEauthorrefmark{5}Intel eric.barton@intel.com}
}
\maketitle

@@

%To address these challenges,
A joint effort between the US Department of
Energy's Office of Advanced Simulation and Computing and Advanced Scientific
Computing Research commissioned a project to develop a design and prototype for
an IO stack suitable for the extreme scale environment. It will be referred to
as the Fast Forward Storage and IO (FFSIO) project. This is a joint effort led
by Lawrence Livermore National Laboratory, with the DOE Data Management Nexus
leads Rob Ross and Gary Grider as coordinators and contract lead Mark Gary. The
participating labs are LLNL, SNL, LANL, ORNL, PNL, LBNL, and ANL.  Additional
industrial partners contracted include the Intel Lustre team, EMC, DDN, and the
HDF Group. This team has developed a specification
set~\cite{fastforward:2014:docs} for a future IO stack to address the
identified challenges. The first phase completed in 2014 with a second phase
currently getting underway. The core focus of the first phase was basic
functionality and design. While an idealized potential system would be the
perfect target architecture, the reality of budgets has tempered many of the
decisions. For example, extensive availability of NVRAM or SSDs on all of the
compute nodes is currently not economically feasible limiting some of the
potential design choices.  With this in mind, the second phase will refine this
design incorporating fault recovery and other features missing from the first
phase.

@@

%Overall, the architecture shifts from the idea of files and directories to
%containers of objects. This shift avoids the bottlenecks related to the POSIX
%files and directories structure such as file creation serialization, the
%file count in a directory limitation and impact, and the limited
%semantics of a byte stream. Instead, the new interface focuses on high-level
%data models and their properties and relationships. This concept permeates the
%entire IO stack.

%In addition to addressing the traditional scientific workload, this project
%seeks to expand functionality to better support Big Data type applications. The
%key idea is to support Arbitrary Connected Graphs (ACGs) such as those used in
%Map-Reduce systems. Key system features are introduced to efficiently support
%these computing models in addition to the typically bursty IO loads of more
%traditional HPC applications. These features are not discussed for space
%reasons.

@@

The rest of the paper is organized as follows. An overview of related work is
presented first in Section~\ref{sec:related}. Section~\ref{sec:end-user}
discusses the programmatic interface end users will see when interacting with
the storage array.
%This will be discussed in the context of the HDF5 based
%example library used for the functionality demonstration.
Section~\ref{sec:iof}
briefly discusses the motivation and proposal for the IO forwarding layer.
Section~\ref{sec:iod} describes the IO Dispatcher layer and the broad
functionality it offers.
%This will detail the pieces of the layer that are
%potentially optional and mention the cross-cutting features discussed in a
%later, cross-cutting section.
Section~\ref{sec:daos} discusses how the DAOS
layer functions.
%As with the IOD layer, the cross-cutting features will be
%mentioned, but discussed more fully in the cross-cutting section.
The VOSD layer is discussed in Section~\ref{sec:vosd}.
%In particular, the mapping
%between the DAOS and VOSD layers are explored as it pertains to the physical
%storage.
Next is an exploration of cross-cutting features like transactions and
metadata management in Section~\ref{sec:broader}.
%Since these and other
%features are spread across multiple layers, it makes more sense to discuss them
%independently once an understanding of the overall structure has been
%presented.
A demonstration of the functionality is presented in
Section~\ref{sec:evaluation}.
%This shows that the prototype system based on the
%proposed design can function.
The paper is concluded in
Section~\ref{sec:conclusion} with a summary of the broad issues covered in the
paper.

@@

\item
  API extensions to support new functionality provided by the FFSIO project.
  This includes calls for managing asynchronous request lists, performing
  asynchronous operations, creating and managing transactions, end-to-end data
  integrity, and data type and functions to support the big data oriented functionality more
  efficiently than the current API.

@@

Since HDF5~\cite{hdf5} has traditionally offered an interface focused on files and the
internal data types, such as datasets, these concepts must be mapped onto the
proposed FFSIO data storage concepts.  This mapping is shown in
Table~\ref{tab:mapping}

\begin{table}[ht]
%    \vspace{-0.10in}
    \centering
    \caption[HDF5 to FFSIO Mapping]{HDF5 Data Model to FFSIO Data Model Mapping}
    \bigskip
%    \vspace{-0.15in}
    \begin{tabular}{|r|r|}
\hline
HDF5 & FFSIO\\
\hline
file & container \\
dataset & array \\
group & key-value store \\
attribute(s) & key-value store \\
\hline
    \end{tabular}
    \label{tab:mapping}
\end{table}

@@

The core idea for IOD is to provide a way to manage IO load that is
separate from the compute nodes and the storage array. Communication intensive
activities, such as data rearrangement, can be moved to the IOD layer
reducing the number of participants and message count. IOD has three main
purposes. First, the burst buffers work as a fast cache absorbing write
operations or pre-staging read operations.
%that then trickles out to the central storage array. It can also
%be used to retrieve objects from the central storage array for more efficient
%read operations and offers data filtering to make client reads more efficient.
Second, it offers the transaction mechanism for controlling data set visibility
and to manage faults that could expose an incomplete or corrupt data set to
users.
%These transactions are local to the IOD layer until persisted to the
%DAOS layer eliminating the need for burdening the persistent storage with
%transient data.
Third, data processing operations can be placed in the IOD.
These operations are intended to offer functionality like data rearrangement
and filtering prior to data reaching the central storage array.

%While these ideas are not necessarily new, they are new twists on best of class
%efforts for these technologies. For example, offloading the collective
%two-phase data sieving from the compute nodes to reorganize data has proven
%effective at reducing the total time for writing data due to fewer participants
%involved in the communication patterns~\cite{lofstead:2011:nessie-staging}.
%Beyond these broad items, there are many important details some of which are
%examined in more detail below.

@@

\textbf{Container}
%As mentioned above, the concept of
A container is similar to that of a file in a traditional file system. However,
rather than being in a directory structure, each container essentially is
stored in a hash-space allowing direct access to
any container without regard to the current organizational context of the
file system.
%For example, there is no need to navigate a directory hierarchy
%to name a particular container.
%
%Functionally, a container plays the same role as a file in that it holds a
%collection of presumably related data intended to be accessed and manipulated
%as a unit.
Since this is extended from HDF5 files, the container could also be
viewed as a directory tree of objects where each directory entry specifies
either a sub-directory (group) or some data or attribute. For the IOD layer, it
is a collection of objects. For HDF5, interpreting the objects builds the
structure.

\textbf{Key-Value Store}
This is the base type for the container. Since the container represents
something akin to HDF5 files, everything is stored within a hierarchical
namespace. The root namespace is represented by the base key-value store and
contains a list of all of the objects for this portion of the namespace as well
as additional key-value objects representing sub-groups for the hierarchy. Each
of those key-value store objects works identically.  Attributes are stored in a
key-value store object, but use the
multi-dimensional array and blob objects to store the values for the
attributes.

\textbf{Multi-Dimensional Array}
By treating arrays as a special case separate from blobs, additional
opportunities are enabled. For example, by knowing that an object is an array,
proper slicing of that array onto IO nodes can be done without involving higher
levels of the IO stack.

\textbf{Blob}
All other data is stored as a stream-of-bytes without regard to the actual
data type.

\subsection{Multi-Dimensional Arrays}

@@

\begin{itemize}
\item
  \textbf{contiguous}. fixed chunking, distributed in a round-robin
  fashion across the IO nodes.
%\item
  \textbf{(2)chunked}. same as above but with irregular (sparse) chunking.
%\item
  \textbf{(3)user-defined}. either contiguous or chunked, but user specifies
  where to place each individual shard.
\end{itemize}

@@

In the case of the written IOD design, it describes a fixed-sized staging area
that is partitioned on a per-application basis. As part of an application
being deployed into the platform, each application will be allocated a fixed
number of IO nodes for exclusive use during the application run. This provides
guarantees about how much burst buffer space and processing capability will be
available for the applications.
%
%Future work will generalize this model to potentially support dynamic IO node
%allocation and examine the possibility of oversubscription. It will be strictly
%necessary to consider shared IO nodes for cases where the number of deployed
%applications exceeds the number of IO nodes.
This first phase focuses on
extreme scale application runs that use the vast majority of a platform rather
than a capacity cluster where end-to-end performance is a lesser concern.

@@

The Distributed Asynchronous Object Storage layer serves as the traditional
parallel file system interface layer for the storage devices. This is the
consistent, global view of the underlying devices represented in this stack
by the VOSD layer.
This is the layer where the container/object model is translated into the
physical storage requirements dictated by the physical storage underneath (the
VOSD layer). The two key design elements of this layer are the handling of
epochs and the mapping of containers and objects to the underlying storage.

@@

%At a more detailed level, the design for VOSD is an increment beyond the
%current Lustre Object Storage Device design to incorporate the idea of shards
%and the versioning aspects of transactions/epochs. For every DAOS shard, the
%VOSD has information for storing and accessing the currently committed version,
%the Highest Committed Epoch, as well as a staging dataset representing the
%next version of the object being stored. Both of these are combined in a shard
%root.
%
%For data integrity, an intent log is maintained as part of the underlying file
%system enabling fault recovery.
%
%Beyond the functionality to incorporate and expose the copy-on-write nature
%of the underlying file system and the semantics for storing and processing
%shards and their associated epochs, this is largely an evolution of the
%existing Lustre OSD layer.

@@

In the subsections that follow, we examine transactions and epochs, metadata
management, and function and analysis shipping.

\begin{figure*}[htbp!]
\centering
%\vspace{-0.10in}
\subfigure[Write Size]{\label{fig:write-size}\includegraphics[width=\columnwidth]{images/write-size.png}}
\subfigure[Read Size]{\label{fig:read-size}\includegraphics[width=\columnwidth]{images/read-size.png}}
%\vspace{-0.10in}
\caption{Functionality Demonstration Validation for Data Sizes}
\label{fig:eval-size}
%\vspace{-0.2in}
\end{figure*}

@@

The second form is called multi-leader and has the IOD layer manage the
transactions. In this case, when the transaction is created, a count of clients
is provided to the IOD layer. As clients commit their changes to the container,
the reference count is reduced. Once the count reaches 0, the transaction is
automatically committed. Aggregation into a smaller set of leaders is also
possible.

@@

\subsection{Metadata Management}
%Metadata management has been a perennial challenge for parallel storage
%%systems.  Eliminating metadata management as a special case and instead
%treating it just as data is a central design goal of the Fast Forward project.
%FFSIO uses a hybrid approach to metadata management that is halfway between
%providing no inherent metadata support and having a fully integrated, but
%separate metadata management system.

%Eliminating metadata as a core component of a file system is not new. It has
%been explored as part of the Light Weight File Systems
%project~\cite{oldfield:lwfs}. In LWFS, the metadata service is explicitly
%limited to a user task with the storage layer limited to data
%storage/retrieval, authorization, and authentication. This approach proved
%workable. Using this hybrid approach is less common~\cite{weil:2006:ceph} and
%introduces other issues.

@@

While the metadata design is not fully defined, there are a few things that
are intended. For example, there will be a standard, well-known container that
is the system metadata. This includes the list of all other containers. This
container is treated like any other data in the system and striped as
appropriate. Unfortunately, this still couples the metadata to a single object
that must serialize access.
%If the metadata, including information about
%striping and other data layout operations were separated completely from the
%data path, more scalable throughput could be achieved.
The real challenge of
this is introduced by the IOD, DAOS, and VOSD layers collectively. Each of
these requires some different metadata storage and the migration is invisible
to the user.  Supporting fully independent metadata with this model is
difficult. Serious thought on how to do this effectively outside the data path
will be considered for phase two.

@@

\section{Acknowledgements}
Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.
